\documentclass{harnon-cv}
\usepackage{verbatim}
\usepackage{numprint}

% personal details
\yourname{Bin Lan}
\yournumber{(475) 302-0829}
\youraddress{Stamford, CT}
\youremail{lanxx019+job@gmail.com}
\yourgithub{https://github.com/lanxx019}
\yourlinkedin{https://www.linkedin.com/pub/bin-lan/75/b62/46a}

%personal statement
\recenthistory{I love technology. I love programming. Everyday, I can discover something new that makes me love this dynamic field a little bit more. I am a dependable and hard working team player. I like to spend my non-technical time on basketball and \textit{Scifi} movies.}

\begin{document}

\maketitle

\begin{comment}
% Objective
\addheadertext{Objective}
A challenging position in the field of Software Engineering.
\end{comment}


% Experience
\addheadertext{Experience}
\starttimeline
\timelineitem{01/2019 - Now} {
    \addsubheader{Software Engineer, Google}
    \addtimelinebullet{Building systems to scale Google's workforce.}
}
\timelinespacer
\timelineitem{10/2016 - 01/2019} {
    \addsubheader{Staff Software Engineer, Transfix}
    \addtimelinebullet{Built integrated solution for automated truck load booking.}
    \addtimelinebullet{The legacy monalithic app is based on RoR.}
    \addtimelinebullet{Built several micro services using AWS stack, e.g. FIFO SQS, Kinesis, Lambdas/Step Functions.}
}
\timelinespacer
\timelineitem{02/2016 - 10/2016} {
    \addsubheader{Senior Software Engineer, Fitbit, Inc.}
    \addtimelinebullet{Worked in Fitbit commerce platform for product fulfillment service.}
    \addtimelinebullet{Integrated PayPal payment into the system.}
    \addtimelinebullet{Built the interface for extended warranty purchase flow with SquareTrade.}
}
\timelinespacer
\timelineitem{07/2013 - 02/2016} {
    \addsubheader{Java Application Engineer, MongoDB, Inc.}
    \addtimelinebullet{Worked in the MongoDB Cloud team as a fullstack engineer.}
    \addtimelinebullet{Utilized Backbone and Mariontted to construct complex UI for MongoDB cluster monitoring page.}
    \addtimelinebullet{Designed the Single Sign On system for the MongoDB Cloud platform.}
    \addtimelinebullet{Maintained the Cloud Platform core system.}
}
\timelinespacer
\timelineitem{04/2011 - 07/2013} {
    \addsubheader{Software Engineer, SilverSky}
    \addtimelinebullet{Built REST API for the Archive system using Java and Jersey.}
    \addtimelinebullet{Implemented company's new portal for different services using PHP, Symfony2 framework, and Oracle\textsuperscript{\textregistered} 10$g$.}
    \addtimelinebullet{Designed and implemented a scalable SMTP server that archives \npthousandsep{,}\numprint{200000000} messages and 30TB data every month.}
    \addtimelinebullet{Maintained and improved company's most profitable product, Archive Continuity portal.}
}
\timelinespacer
\timelineitem{05/2010 - 04/2011} {
    \addsubheader{Software Engineer, Ventus Networks}
    \addtimelinebullet{Implemented a web portal that monitors thousands of routers and ATMs.}
    \addtimelinebullet{Used C/C++, JavaScript, JQuery, and MySQL\texttrademark\space database.}
}
\timelinespacer
\timelineitem{10/2008 - 05/2010} {
    \addsubheader{R\&D Engineer, SilverSky}
    \addtimelinebullet{Migrated PTRobot API to Java using JNI and automated the CD/DVD burning service.}
    \addtimelinebullet{Ported Microsoft\textsuperscript{\textregistered} Messaging API to JAVA using JNI, also implemented a EML/PST converter on top of it.}
    \addtimelinebullet{Implemented a text extraction library using Java, JNI, and Microsoft\textsuperscript{\textregistered} IFilter interface, which can extract text data for different binary formats.}
}
\timelinespacer
\timelineitem{09/2006 - 05/2008} {
    \addsubheader{Teaching Assistant, University of Minnesota Duluth}
    \addtimelinebullet{Lectured weekly laboratory for different Computer Science courses.}
    \addtimelinebullet{Graded programming assignments.}
}
\stoptimeline\par

% Technical Skills
\addheadertext{Technical Skills}
\begin{itemize}\itemsep1pt
\item Proficient in Java. Working experience with PHP, javascript, C/C++.
\item Understand Java Thread model, JDBC framework, and MVC pattern. Used multiple web frameworks, such as Struts, Symfony2, and Jersey.
\item Worked on MySQL\texttrademark, Oracle\textsuperscript{\textregistered} 10$g$, and Microsoft\textsuperscript{\textregistered} SQL server.
\item Use Linux since 2001. Know how to customize and compile kernel. Played with Gentoo, Debian, and other flavors.
\item Working experience with various version control system, including SVN, and Git.
\item Interested in REST, JVM languages, and NoSQL.
\end{itemize}\par

% Education
\addheadertext{Education/Certification}
\starttimeline
\timelineitem{09/2009}{
    \addsubheader{Sun\textsuperscript{\textregistered} Certified Web Component Developer}
}
\timelinespacer
\timelineitem{06/2008}{
    \addsubheader{Sun\textsuperscript{\textregistered} Certified Java Developer}
}
\timelinespacer
\timelineitem{05/2008}{
    \addsubheader{M.S. Computer Science}
    \addtimelinebullet{University of Minnesota Duluth}
    \addtimelinebullet{GPA: 3.5/4.0}
}
\timelinespacer
\timelineitem{05/2005}{
    \addsubheader{B.S. Computer Science}
    \addtimelinebullet{University of Wisconsin Superior}
    \addtimelinebullet{GPA: 3.3/4.0}
}
\stoptimeline

% School Projects -- Might not show
\begin{comment}
\addheadertext{School Projects}
\addsubheader{Grounder for SAT Solver}
\begin{itemize}\itemsep1pt
\item Implemented a new logical problem modeling language using Java and Javacc.
\item Used directed acyclic tree to organize language tokens.
\item Translate the input logical problem into CNF clauses.
\end{itemize}\par
\addsubheader{N-gram Pattern}
\begin{itemize}\itemsep1pt
\item Team project to use distributed environment to retrieve information from Google N-gram data.
\item Contributed to the design of the underlying distributed data structure in C++.
\item Implemented the parallel union-find algorithm to analyze the topology of N-gram network.
\item Managed the final code integration and testing.
\item Only team successfully deliver the end result.
\end{itemize}\par
\addsubheader{Virtual Object Manipulator}
\begin{itemize}\itemsep1pt
\item Designed a prototype system which allows user to interact with virtual 3D objects using their own hands.
\item Integrated ARToolKit to recognize hand gestures.
\item Implemented 3D scenes and objects using OpenScene Graph.
\item Designed the algorithm for manipulating virtual objects.
\end{itemize}\par
\stoptimeline
\end{comment}


% Other Skills
\addheadertext{Other Skills}
Fluent in Chinese

\end{document}
